### 2021-04-17 paper/maxdet.tex
Small typos corrected

\section{Independence, maximal determinant, and entropy}
\subsection{A simpler problem}
Before we answer the question of the last section in full generality we look at a simpler case to determine how we want to complete the matrix $M$. As in the previous section we denote by $I$ be the set of stochastic processes. For this simple case we assume that there are two sets $\alpha, \beta\subset I$ with $\alpha\cup\beta = I$ and $\alpha\cap\beta = \gamma\ne \emptyset$. For any $\delta\subset I$ we will denote by
\begin{equation}
	M[\delta]
\end{equation}
the principal submatrix of $M$ with row and column indices in $\delta$. In general we will denote for $\delta,\eta\subset I$ by 
\begin{equation}
	M[\delta,\eta]
\end{equation}
the submatrix of $M$ with row indices in $\delta$ and column indices in $\eta$. We assume that
\begin{equation}
	M[\alpha] \text{\ and\ } M[\beta] 
\end{equation}
are known. The matrix $M$ thus has the form
\begin{equation}\label{eqn.corrmatrix}
	M = \begin{pmatrix}
		C & D & W \\
		D^T & E & F \\
		W^T & F^T & G
	\end{pmatrix}.
\end{equation}
Using the notation that we have just introduced we have
\begin{align}
	M[\alpha] & = \begin{pmatrix}
		C & D  \\
		D^T & E 
	\end{pmatrix} \\
	M[\beta] & = \begin{pmatrix}
		E & F  \\
		F^T & G 
	\end{pmatrix} \\
	M[\gamma] & = E \\
	M[ \alpha-\gamma, \alpha-\gamma] & = C \\
	M[ \alpha-\gamma, \gamma] & = D \\
	M[ \alpha-\gamma, \beta-\gamma] & = W \\
	M[ \gamma, \beta-\gamma] & = F \\
	M[ \beta-\gamma, \beta-\gamma] & = F
\end{align}
The part of the matrix that we need to determine is $W$. If the overlap $E$ didn't exist we would just set $W=0$ and thus ensure that $\alpha$ and $\beta$ are independent. This is the desirable result because any other choice would assume information about the correlation between $\alpha$ and $\beta$ that we do not have. Since the overlap $E$ is present, we have to make a different choice.

>>>>

\section{Independence, maximal determinant, and entropy}
\subsection{A simpler problem}
Before we answer the question of the last section in full generality we look at a simpler case to determine how we want to complete the matrix $M$. As in the previous section we denote by $I$ be the set of stochastic processes. For this simple case we assume that there are two sets $\alpha, \beta\subset I$ with $\alpha\cup\beta = I$ and $\alpha\cap\beta = \gamma\ne \emptyset$. For any $\delta\subset I$ we will denote by
\begin{equation}
	M[\delta]
\end{equation}
the principal submatrix of $M$ with row and column indices in $\delta$. For two sets $\delta,\eta\subset I$ we denote by 
\begin{equation}
	M[\delta,\eta]
\end{equation}
the submatrix of $M$ with row indices in $\delta$ and column indices in $\eta$. We assume that
\begin{equation}
	M[\alpha] \text{\ and\ } M[\beta] 
\end{equation}
are known. The matrix $M$ can then be written in the form
\begin{equation}\label{eqn.corrmatrix}
	M = \begin{pmatrix}
		C & D & W \\
		D^T & E & F \\
		W^T & F^T & G
	\end{pmatrix},
\end{equation}
where we make the following identifications:
\begin{align}
	M[\alpha] & = \begin{pmatrix}
		C & D  \\
		D^T & E 
	\end{pmatrix} \\
	M[\beta] & = \begin{pmatrix}
		E & F  \\
		F^T & G 
	\end{pmatrix} \\
	M[\gamma] & = E \\
	M[ \alpha-\gamma, \alpha-\gamma] & = C \\
	M[ \alpha-\gamma, \gamma] & = D \\
	M[ \alpha-\gamma, \beta-\gamma] & = W \\
	M[ \gamma, \beta-\gamma] & = F \\
	M[ \beta-\gamma, \beta-\gamma] & = F
\end{align}
The part of the matrix that we need to determine is $W$. If the overlap $E$ didn't exist we would just set $W=0$ and thus ensure that $\alpha$ and $\beta$ are independent. This is the desirable result because any other choice would assume information about the correlation between $\alpha$ and $\beta$ that we do not have. Since the overlap $E$ is present, we have to make a different choice.
